### 2014-06-12 manuscript/latitudepaper.tex
Finished results.

Creating networks describing ecologically important interactions (e.g. food
webs composed of feeding links) provides a powerful way to explore differences
in community structure as networks provide a rich set of metrics that can be
used to compare structure across ecosystems (Williams & Martinez, 2000, Olesen
& Jordano, 2002, Stouffer et al., 2005, Reide et al., 2010). Such comparisons
have revealed that the structure of biological networks is generally tightly
constrained (Riede et al., 2010) and that it may be possible to reduce the
plethora of network variables to a few major descriptive dimensions (Vermaat
et al., 2009). In particular, characteristic changes in structural properties
with species richness and connectance (number of links/number of species2)
have suggested scale-dependence (Riede et al., 2010), which here refers to the
strong dependence of network properties, such as fractions of
species in different trophic groups, on the species richness or connectance of
the networks. Therefore it is likely that much variation in network structure
can be explained by variation in these two properties (Vermaat et al., 2009).

@@

Second, we analysed the scaling relationships between the remaining XX food-
web parameters and connectance and species richness. We used a series of
generalized linear models with a food-web parameter as the dependent variable
and latitude, ecosystem type, and their interactions with connectance and
species richness as independent variables. (parameter ~
latitude*ecotype*(log10(connectance)+log10(species richness))). For food web
properties that were proportions, we used general linear models with a
binomial distribution. All other food web properties were log-transformed
except for motif frequencies, where many webs had zero frequencies of at least
some motifs. When modelling the standard deviation of generality, this
required the removal of 5 webs, all with 12 or fewer species, which had
standard deviations of generality of 0. These full models were then
systematically reduced using R function dredge \cite{} in package MuMIn
\cite{} in order to isolate the model with the highest AIC.

@@

The scaling relationships of many food-web properties changed across latitude.
(need to look up difference between change in slope and change in int.) Mean
trophic level scaled with species but not connectance and had both slope and
intercept effects of latitude and ecotype. Maximum trophic level scaled with
both species-richness and connectance, with the species-richness relationship
having both slope and intercept effects of latitude while the connectance
relationship had both slope and intercept effects of ecotype. Similarly, the
scaling of generality with species-richness has both slope and intercept
effects of latitude, as well as an intercept effect of ecotype.

The scaling of motif frequencies with connectance varied across ecotypes for
most motifs (specifically motifs 102, 108, 110, 14, 238, 46, 74, and 78) with
both intercept and slope effects. Scaling relationships with species-richness
did not change. Latitude had not effect on the scaling relationships of these
motifs. For three motifs (12, 36, and 6), scaling was not associated with
either latitude or ecotype. The frequency of the remaining motif (108) did not
scale with species richness. The scaling of this motif's frequency with
connectance did vary with latitude, although this relationship was not
significant.  Overall, therefore, we conclude that motif structure does not
change across latitude.

[Table of results]

>>>>

[[Shorten this up]]

Creating networks describing ecologically important interactions (e.g. food
webs composed of feeding links) provides a powerful way to explore differences
in community structure as networks provide a rich set of metrics that can be
used to compare structure across ecosystems (Williams & Martinez, 2000, Olesen
& Jordano, 2002, Stouffer et al., 2005, Reide et al., 2010). Such comparisons
have revealed that the structure of biological networks is generally tightly
constrained, particularly by relationships between species richness or connectance
(the proportion of possible links that are realized)
which suggest scale-depence (Riede et al., 2010), which here refers to the
strong dependence of network properties, such as fractions of
species in different trophic groups, on the species richness or connectance of
the networks. Therefore it is likely that much variation in network structure
can be explained by variation in these two properties (Vermaat et al., 2009).

@@

Second, we analysed the scaling relationships between the remaining XX food-
web parameters and connectance and species richness. We used a series of
generalized linear models with a food-web parameter as the dependent variable
and latitude, ecosystem type, and their interactions with connectance and
species richness as independent variables. (parameter ~
latitude*ecotype*(log10(connectance)+log10(species richness))). For food web
properties that were proportions, we used general linear models with a
binomial distribution. All other food web properties were log-transformed.
When modelling the standard deviation of generality, this
required the removal of 5 webs, all with 12 or fewer species, which had
standard deviations of generality of 0. These full models were then
systematically reduced using R function dredge \cite{} in package MuMIn
\cite{} in order to isolate the model with the highest AIC. These best-fitting models were 
then examined in detail.

@@

In this data set, none of the best fit models for species richness, connectance, or links per species included an 
effect of latitude, although all three properties varied across ecosystem types. [[Table or something]]

The best-fit models for most food-web properties exhibited scaling relationships with species-richness and/or 
connectance. Notable exceptions were the proportions of basal resources, herbivores, and omnivores, which varied only 
across year published; and the proportions of top predators and intermediate consumers, which varied with connectance 
and species richness and connectance (respectively) although not significantly.

For the food-web properties that did scale with species-richness or connectance, most of these relationships were 
constant over latitude. Latitude terms were not included in the best-fit models for vulnerability, SD of generality or 
SD of links. SD of vulnerability showed a weak negative relationship with latitude ($\Beta$=-0.001, $p$=0.056), 
and path length increased with increasing 
latitude ($\Beta$ = 0.005, $p$=0.045) but neither latitude effect affected any scaling with species richness or 
connectance.

The scaling rules of mean and maximum trophic level and generality varied over latitude. 
Maximum trophic level increased with 
latitude ($\Beta=0.011$, $p$=0.011), but this relationship was weakened as species richness increased ($\beta$=-0.008, $
p$=0.011). Similarly, maximum trophic level increased with species richness ($\beta$=0.430, $p$=0.003) except at very 
high latitudes. Maximum trophic level decreased with connectance for estuarine food webs ($\beta$=-0.458, $p$=0.021), 
varied little in lakes ($\beta$=-0.127, $p$=0.192), and increased with connectance in marine, stream, and terrestrial 
food webs ($\beta$=0.219, $p$=0.005; $\beta$=0.249, $p$<0.001; and $\beta$=0.337, $p$=0.002, respectively). Taken 
together, these effects resulted in an increase in maximum trophic level with latitude at low species richnesses across 
all ecotypes and decreasing maximum trophic level with latitude at high species richness across all ecotypes 
(Fig. \ref{}. At moderate levels of species richness, trophic level increased with latitude for estuarine webs, showed 
little change for lake webs, and decreased for all other ecotypes.

Qualitatively similar trends were observed for mean trophic level. Mean trophic level increased with latitude 
($\beta$=0.0109, $p$<0.001) and with species richness ($\beta$=0.616, $p$<0.001), but both trends were weakened by an 
interaction between latitude and species-richness ($\beta$=-0.008, $p$<0.001). The best-fitting model for mean trophic 
level did not include a connectance term. The increase in mean trophic level with species richness was highest for 
estuarine food webs ($\beta$=0.616, $p$<0.001) and lower for lakes ($\beta$=-0.608, $p$=0.232), streams 
($\beta$=0.238, $p$<0.001), terrestrial food webs ($\beta$=0.217, $p$=0.002), and marine food webs 
($\beta$=0.133, $p$<0.001).

Generality showed the opposite trend, decreasing with increasing latitude ($\beta$=-0.017, $p$=0.003). This decrease 
was counteracted by a positive interaction between latitude and species richness ($\beta$=0.013, $p$=0.003), with the net result that generality increased with latitude for most ecotypes and species richnesses (Fig. \ref{}).
The main effect of species richness on generality varied across ecotypes. Generality decreased with increasing species 
richness for estuarine webs ($\beta$=-0.058, $p$=0.003) and increased for lakes ($\beta$=0.220, $p$=0.245), 
streams ($\beta$=0.543, $p$<0.001), terrestrial ($\beta$=0.603, $p$=0.005) and marine webs ($\beta$=0.761, $p$<0.001). 
Generality increased with connectance equally for all ecotypes ($\beta$=0.875, $p$<0.001).

\section*{Discussion}

The tendency of food-web structure to exhibit scaling relationships with both species richness and connectance has been 
well-established \citep{,,,,}. As species richness in particular is also know to vary systematically over latitude 
\citep{,,,,}, intuitively one might suspect that the scaling relationships of other food web properties might also vary
over latitude \citep{}. However, we found that only four of XX food web properties varied significantly over latitude, 
and that only the scaling relationships of trophic level and generality varied from the tropics to the poles.

A study of plant-animal mutualistic networks found the opposite trend to that observed here, that generality decreased 
with increasing latitude while increasing with increasing plant diversity \citep{Schleuning2012}. Unfortunately this 
study did not examine changes in scaling relationships over latitude... Regardless, this may indicate that food webs 
and mutualistic networks vary differently over latitudinal gradients of productivity, temperature, etc. 
\citet{Schleuning2012} propose that the latitudinal specialization gradient in mutualists derives from the gradient in 
plant diversity, as high resource diversity may lead to more generalized consumers. As species richness in the food 
webs in our dataset did not vary over latitude, it seems unlikely that this is the mechanism driving increased 
generality in high-latitude food webs. As we also observed an increase in both mean and maximum trophic level with 
latitude, it is possible that high-trophic level species are also more apt to be generalists. Generalism may be an 
important strategy for high-level consumers as their prey may be scarce or seasonal \citep{}.

[[other scaling paper]]

The overall consistency of scaling laws over latitude is remarkable and suggests that food webs worldwide assemble 
along similar ``rules'' regardless of temperature, productivity, or other latitudinal gradients. However, the changing
scaling laws for generality and trophic level suggest that there are also key differences in the ways that food webs 
are configured in the tropics and at higher latitudes. Importantly, the opposing trends for generality in food webs 
and mutualistic networks may suggest that latitude imposes different pressures on mutualistic versus antagonistic 
interactions between species. [[Need a punchier conclusion]]
